Stable individual differences in strategies within, but not between, visual search tasks

### 2018-11-29 Manuscript/manuscript.tex
more small edits

The results show that the correlations between the strategy metrics in the three tasks (Figure \ref{fig:all_the_cor}) are weak. Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks. Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from task to task, the upper bound of $r=0.30$ means that this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments. Surprisingly, however, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually, which range from [x to x].

There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise. The high test-retest correlations on each of the individual visual search tasks rules out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation. One might have expected reaction time to be at least modestly correlated from one search task to the next, even in the absence of correlations in strategy, as a general factor like an individual's motivation or conscientiousness might lead to better or worse overall performance across all the tasks. However, even reaction times were not highly correlated between tasks. What we did observe were correlations between our measures of strategy and reaction time within each task, suggesting our strategy metrics are predictive of search performance, and reinforcing the interpretation that an individual who is strategic in one task is not necessarily strategic in the others.

@@

>>>>

The results show that the correlations between the strategy metrics in the three tasks (Figure \ref{fig:all_the_cor}) are weak. Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks. Even if we optimistically take all data together as suggesting a robust correlation in reaction times from one task to another, the mean correlation over the three tasks is only $r = 0.2$, implying that this correlation accounts for  $R^2 = 0.04 = 4\%$ an individual's performance.

@@

We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments. Surprisingly, however, the between-paradigm correlations give $R^2 = 0.04$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually, which range from a lower bound of 0.58 to an upper bound of 0.92 .

There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise. The test-retest correlations on each of the individual visual search tasks rules out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation. One might have expected reaction time to be at least modestly correlated from one search task to the next, even in the absence of correlations in strategy, as a general factor like an individual's speed-accuracy trade-off, motivation or conscientiousness might lead to better or worse overall performance across all the tasks. However, even reaction times were not highly correlated between tasks. What we did observe were correlations between our measures of strategy and reaction time within each task, suggesting our strategy metrics are predictive of search performance, and reinforcing the interpretation that an individual who is strategic in one task is not necessarily strategic in the others.

@@

\section*{Acknowledgements}

We would like to thanks Anna Nowakowska, {\'A}rn Kristj{\'a}nsson and Ian Thornton for sharing data and their helpful comments and suggestions. We would like to thank Charles Rigitano and Jacqueline Von Seth who helped with data collection. We acknowledge the funding support of the James S. McDonnell Foundation (Scholar Award to ARH).
